An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-07-08 jmiv.tex
fatigue

\daniel{In our experiments, the best results are obtained by executing DCE algorithm with $m$ equal to $r$, where $r$ is
  the estimation ball radius (see figure \ref{fig:mx-square-flow} ). We observe that Elastica may increase after some
  iterations if chosen radius is too large, as in the case of the triangle in figure \ref{fig:mx-flow-gs-radius-effect}
  in which the flow converges to a single point. We conjecture that an appropriated value for the radius should be given
  by the shape reach.  The produced flow has no difficulties in handling changes on topology, and it presents different
  speeds for regions with low and high curvature values, as illustrated in figure
  \ref{fig:mx-speed-variation-hole-filling}.}

@@

Energy $E_m$ is non-submodular and optimizing it is a difficult
problem, which constrains us to use heuristics and approximation
algorithms. The QPBO method \cite{rother07qpbo} transforms the
original problem in a max-flow/min-cut formulation and returns a full
optimal labeling for submodular energies. For non-submodular energies
the method is guaranteed to return a partial labeling with the
property that the set of labeled variables is part of an optimal
solution. That property is called partial optimality.

In practice, QPBO can leave many pixels unlabeled. There exist two
extensions of QPBO that alleviate this limitation: QPBOI (improve) and
QPBOP (probe). The first is an approximation method that is guaranteed
to not increase the energy, but we lost the property of partial
optimality. The second is an exact method which is reported to label
more variables than QPBO.

The percentage of unlabeled pixels by QPBOP for $E_1$ is quite high,
but the percentage decreases to zero as we set $m$ equal to
$r$. Therefore, we are more confident to take the solution for values
of $m$ close to $r$. However, the way it varies across $m$ values
differs from shape to shape, as is illustrated in figure
\ref{fig:unlabeled-versus-iterations}. We also noticed that, for
$m=r$, all the pixels were labeled, \daniel{which may indicate that $E_r$ is an an easy 
instance of the general non-submodular energy $E_m$, but this remains to be proved. The number of pairwise
terms in $E_r$ is roughly half of those in $E_1$ (see figure \ref{fig:ratio-pairwise-terms}).}

>>>>

{In our experiments, the best results are obtained by executing DCE algorithm with $m$ equal to $r$, where $r$ is
  the estimation ball radius (see figure \ref{fig:mx-square-flow} ). We observe that Elastica may increase after some
  iterations if chosen radius is too large, as in the case of the triangle in figure \ref{fig:mx-flow-gs-radius-effect}
  in which the flow converges to a single point. We conjecture that an appropriated value for the radius should be given
  by the shape reach.  The produced flow has no difficulties in handling changes on topology, and it presents different
  speeds for regions with low and high curvature values, as illustrated in figure
  \ref{fig:mx-speed-variation-hole-filling}.

@@

Energy $E_m$ is non-submodular and optimizing it is a difficult problem, which constrains us to use heuristics and
approximation algorithms. The QPBO method \cite{rother07qpbo} transforms the original problem in a max-flow/min-cut
formulation and yields a full optimal labeling for submodular energies. For non-submodular energies the method is
guaranteed to return a partial labeling with the property that the set of labeled variables is part of an optimal
solution. That property is called partial optimality.

In practice, QPBO can leave many pixels unlabeled. There exist two extensions to QPBO that alleviate this limitation:
QPBOI (improve) and QPBOP (probe). The first is an approximation method that is guaranteed to not increase the energy,
but loses the property of partial optimality. The second is an exact method which is reported to label more variables
than QPBO.

The percentage of unlabeled pixels by QPBOP for $E_1$ is quite high, but the percentage decreases to zero as we set $m$
equal to $r$. Therefore, we are more confident in taking the solution for values of $m$ close to $r$. However, the way it
varies across $m$ values differs from shape to shape, as is illustrated in figure
\ref{fig:unlabeled-versus-iterations}. We also noticed that, for $m=r$, all the pixels were labeled, {which may
  indicate that $E_r$ is an an easy instance of the general non-submodular energy $E_m$, but this remains to be
  proved. The number of pairwise terms in $E_r$ is roughly half of those in $E_1$ (see figure
  \ref{fig:ratio-pairwise-terms}).
